Spin canonical divisors of log stacky curves

### 2015-06-22 stacky_write_up/spin_cring.tex
add halfcan to ex, check gens and rels in ex

\begin{thm}
\label{}
Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$. Then $I_L$ is generated in degree at most $11$.
\end{thm}
\begin{proof}
Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
$$\begin{tikzcd}
V \otimes H^0((\deg f - 2)L) \ar {r}{f} & H^0((\deg f)L),
\end{tikzcd}$$
we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
So, using the refined version of the basepoint free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$. Therefore,
\begin{align*}
	s_1g + s_2h \equiv s_1s_2\rho + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
\end{align*}
\end{proof}

@@

\begin{lem}
\label{lem:g_0_admissible_cases}
Let $(\sx', \Delta, L')$ be a tame log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$.
Then $R' := R(\sx', \Delta, L')$ is generated as a $k$-algebra by elements
of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree
at most $2e$ and $(\sx', J)$ is admissible for the following cases:

@@

\begin{example}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
We have that $K_{\sx'} \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
We exhibit a (minimal) presentation for $R'$.

@@

By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
and Zureick-Brown \cite{vzb:stacky}),

\[
	H^0 (\sx', \lfloor 21 K_{\sx'} \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) K_{\sx'} \rfloor) \twoheadrightarrow = H^0 (\sx', \lfloor
	d K_{\sx'} \rfloor)
\]

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Also, $\sigma_2$ has saturation $s = 5$ as noted in
Subsection ~\ref{ssec:g_0_saturation}. Thus, $R'$ is generated up to
degree $21 + (s - 1) = 24$.

For $d = 0, 1, 2, \ldots$ we have

\[
	dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
\]

\noindent
so $R'$ must have some generators $x_{1, 3}, x_{1, 5}, x_{1, 7},
x_{1, 7}$. Let $(-ord_{P_1}(x_j), -ord_{P_2}(x_j), -ord_{P_3}(x_j))$
represent the pole orders of $x_i$ at each point. Then these generators
must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
respectively.

>>>>

\begin{thm}
\label{}
Let $X$ be a curve of genus $g \geq 2$ and let $L$ be a divisor with $2L \sim K$. Then $I_L$ is generated in degree at most $11$.
\end{thm}
\begin{proof}
Suppose $f \in I_L$ with $\deg f \geq 12$. To complete the proof, it suffices to show $f \in I_{L,d}'$. By Lemma ~\ref{lem:reducing_degree}, it suffices to show $s_1g+s_2h \in I_{L,d}'$. 
Let $V \subset H^0(K)$ be the vector subspace generated by $\phi(s_1)$ and $\phi(s_2)$, and consider the map
$$\begin{tikzcd}
V \otimes H^0((\deg f - 2)L) \ar {r}{f} & H^0((\deg f)L),
\end{tikzcd}$$
we know that $\phi(s_1)\phi(g) + \phi(s_2) \phi(h) \mapsto 0.$
So, using the refined version of the basepoint free pencil trick, as shown in the proof of \cite{saint-donat:proj}[Lemma 2.6], if $\phi(s_1) g + \phi(s_2)h \mapsto 0,$ there exists some $\rho \in k[x_1, \ldots, x_n]$ so that $\phi(\rho) \in H^0((\deg f - 4)L)$ satisfies $\phi(g) = \phi(s_2)\phi(\rho)$ and $\phi(h) = -\phi(s_1)\phi(\rho).$ Therefore, $g \equiv s_2 \rho \bmod I_{k,d-2}$ and $h \equiv -s_1 \rho \bmod I_{k,d-2}$. Therefore,
\begin{align*}
	s_1g + s_2h \equiv s_1s_2\rho + s_2(-s_1 \rho) \equiv 0 \bmod J_{L,d}.
\end{align*}
\end{proof}

@@

\begin{lem}
\label{lem:g_0_admissible_cases}
Let $(\sx', \Delta, \halfcan')$ be a tame log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; 0)$.
Then $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k$-algebra by elements
of degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree
at most $2e$ and $(\sx', J)$ is admissible for the following cases:

@@

\begin{example}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
We have that $\halfcan \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
We exhibit a (minimal) presentation for $R'$.

@@

By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
and Zureick-Brown \cite{vzb:stacky}),
\[
	H^0 (\sx', \lfloor 21 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan \rfloor)
\]

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
when $d \geq 21 + s = 25$ (i.e. $R'$ is generated up to degree 24).

For $d = 0, 1, 2, \ldots$ we have
\[
	\dim H^0 (\sx', d K_{\sx'}) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
\]

\noindent
so $R'$ must have some generators $x_{3, 1}, x_{5, 1}, x_{7, 1},
x_{7, 2}$.

To show that these generate all of $R'$, we need to show that all
$H^0 (\sx', d \halfcan)$ are generated by lower degrees for $d = 6$
and $7 < d \leq 24$. Note that we can again use Max Noether's theorem
(taking saturation into account) to see that

\begin{align*}
	&H^0 (\sx', \lfloor 3 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 3) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
	&H^0 (\sx', \lfloor 7 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 7) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
	\text{ (mod } 7)
\end{align*}

\noindent
are surjective. This reduces the problem to checking generation
in the degrees of the exceptions $d \in \{8, 12, 21\}$.
Checking the remaining cases via pole degrees shows that
these degrees are also generated in lower degrees,
so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.

%Let $(-ord_{P_1}(x_j)$, $-ord_{P_2}(x_j)$, $-ord_{P_3}(x_j))$
%represent the pole orders of $x_i$ at each point. Then these generators
%must have pole orders $(1, 1, 1), (1, 2, 2), (2, 3, 2), (2, 2, 3)$
%respectively.

Furthermore, we can directly see that the relations are given
in degrees $10$ and $14$. In particular, we have a relation
of the form
\[
	a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0
\]

\noindent
in degree $10$ and a relation of the form
\[
	a_1 x_{3, 1}^3 x_{5, 1} + a_2 x_{7, 1}^2 + a_3 x_{7, 1} x_{7, 2} + a_4 x_{7, 2}^2 = 0
\]

\noindent
in degree $14$.

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 1}, x_{7, 2}, x{5, 1}, x_{3, 1}] / I$ with
initial ideal
\[
	in_\prec(I) = < x_{7, 1} x_{3, 1}, x_{7, 1}^2 >
\]

\noindent
generated by quadratics under grevlex with $x_{i, j} \prec x_{k, l}$
if $i > j$ or $i = j$ and $j < l$. These quadratics must also 
determine minimal generators for $I$ by Lemma
~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to degree
$e = 7$ with relations up to degree $2e = 14$, as desired.

Now we check admissibility.
